Early environmental conditions do not impact behavioural flexibility in an invasive and non-invasive lizard species

### 2024-08-30 ms.qmd
Updates

@@

Figures with raw data

@@

Table 3. Number of individuals per treatment and species that reached a learning criterium of 5 consecutive correct choices (n lizards), and the average of trials taken (Trial) together with the standard deviation (sd).  
```{r, tbl-standard_crit, results='asis', out.widht = "26cm"}
#| label: standard_crit
#| tbl-cap: "Number of individuals per treatment and species that reached a learning criterium of 5 consecutive correct choices (n lizards), and the average of trials taken (Trial) together with the standard deviation (sd)."
#
source(here("R", "func.R"))
# Load the data
scrit_df <- clean_df %>%
  group_by(lizard_id,species, trt) %>%
  mutate(
    run_id = cumsum(lag(FC_reversal, default = 0) == 0 & FC_reversal == 1),
    run_length = ave(FC_reversal , run_id, FUN = cumsum) * FC_reversal 
  ) %>%
  filter(run_length >= 5) %>%
  group_by(lizard_id, species, trt) %>%
  slice_min(trial_reversal) %>%  # Get the first trial when the criterion was met
  summarize(
    species = first(species),
    trt = first(trt),
    trial_crit = min(trial_reversal),
    .groups = "drop") %>%
  mutate(trt = factor(trt, 
          levels = c("A_23", "B_23", "A_28", "B_28"), 
          labels = c("Control-Cold", "CORT-Cold", "Control-Hot", "CORT-Hot")),
        species = factor(species,
          levels = c("delicata", "guichenoti"),
          labels = c("L. delicata", "L. guichenoti")))%>%
  group_by(species, trt) %>%
  summarize(
    n = n(),
    mean_trial = format_dec(mean(trial_crit),2),
    des_trial = format_dec(sd(trial_crit),2),
    .groups = "drop") %>%
data.frame()
#
# Create the table
crit_tbl <- flextable(scrit_df) %>%
  set_table_properties(width = 1) %>%
  align(align = "center", part = "all") %>%
  fontsize(size = 10, part = "all") %>%
  set_header_labels(species = "Specie",
                    trt = "Treatment",
                    n = "n lizards",
                    mean_trial = "Mean",
                    des_trial = "sd") %>%
    italic(i = c(1,5), j = 1, italic = TRUE, part = "body") %>% # To have names od species in italics
    flextable::compose(i = c(2:4,6:8), j = 1, value = as_paragraph(""), part = "body") %>% # To remove some of the values in the first column
    hline(i = 4, j = c(1:5), part = "body") %>% # To make some horizontal lines
    autofit()
crit_tbl
```

@@

Checking the effect of age on the learning rate in the associative task.

@@

Plots for the different models of the associative task:  
1.- _L. delicata_    
```{r , plotmod_drr, out.width="70%", fig.align="center"}
bayes_R2(mod_deli)
plot(mod_deli)
```

>>>>

#### Estimates of reversal learning slopes for all the different treatments per each task, specie, and group.

@@

#### Figures with raw data

@@

#### Results using a standard learning criterion of 5 consecutive correct choices  
Table 3. Number of individuals per treatment and species that reached a learning criterium of 5 consecutive correct choices (n lizards), and the average of trials taken (Trial) together with the standard deviation (sd).  
```{r, tbl-standard_crit, results='asis', out.widht = "26cm"}
#| label: standard_crit
#| tbl-cap: "Number of individuals per treatment and species that reached a learning criterium of 5 consecutive correct choices (n lizards), and the average of trials taken (Trial) together with the standard deviation (sd)."
#
source(here("R", "func.R"))
# Load the data
scrit_df <- clean_df %>%
  group_by(lizard_id,species, trt) %>%
  mutate(
    run_id = cumsum(lag(FC_reversal, default = 0) == 0 & FC_reversal == 1),
    run_length = ave(FC_reversal , run_id, FUN = cumsum) * FC_reversal 
  ) %>%
  filter(run_length >= 5) %>%
  group_by(lizard_id, species, trt) %>%
  slice_min(trial_reversal) %>%  # Get the first trial when the criterion was met
  summarize(
    species = first(species),
    trt = first(trt),
    trial_crit = min(trial_reversal),
    .groups = "drop") %>%
  mutate(trt = factor(trt, 
          levels = c("A_23", "B_23", "A_28", "B_28"), 
          labels = c("Control-Cold", "CORT-Cold", "Control-Hot", "CORT-Hot")),
        species = factor(species,
          levels = c("delicata", "guichenoti"),
          labels = c("L. delicata", "L. guichenoti")))%>%
  group_by(species, trt) %>%
  summarize(
    n = n(),
    mean_trial = format_dec(mean(trial_crit),2),
    des_trial = format_dec(sd(trial_crit),2),
    .groups = "drop") %>%
data.frame()
#
# Create the table
crit_tbl <- flextable(scrit_df) %>%
  set_table_properties(width = 1) %>%
  align(align = "center", part = "all") %>%
  fontsize(size = 10, part = "all") %>%
  set_header_labels(species = "Specie",
                    trt = "Treatment",
                    n = "n lizards",
                    mean_trial = "Mean",
                    des_trial = "sd") %>%
    italic(i = c(1,5), j = 1, italic = TRUE, part = "body") %>% # To have names od species in italics
    flextable::compose(i = c(2:4,6:8), j = 1, value = as_paragraph(""), part = "body") %>% # To remove some of the values in the first column
    hline(i = 4, j = c(1:5), part = "body") %>% # To make some horizontal lines
    autofit()
crit_tbl
```

@@

Plots for the different models of the reversal task:  
1.- _L. delicata_    
```{r , plotmod_drr, out.width="70%", fig.align="center"}
bayes_R2(mod_deli)
plot(mod_deli)
```

#### Checking the effect of age on the learning rate in the associative task.

@@
